\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-02-07 intro.tex
adjusted sizes

\begin{scope}[scale=1]
\draw [line] (-1.0,0) circle (0.5);
\draw [line] (-4.0,0) circle (0.5);
\draw [line] (2.0,1) circle (0.5);
\draw [line] (2.0,-1) circle (0.5);
\draw[arw] (-0.5,0) -- (1.5,1.0);
\draw[arw] (-0.5,0) -- (1.5,-1.0);
\draw[arw] (-3.5,0) -- (-1.5,0.0);
\node at (-4.0,0) {$C$};
\node at (-1.0,0) {$C'$};
\node at (2.0,1.0) {$C''_1$};
\node at (2.0,-1.0) {$C''_2$};
\draw [line] (2.0,-1) circle (0.5);
\draw[arw] (-5.0,-2.0) -- (3.0,-2.0);
\node at (-4.0,-2.5) {$k=0$};
\node at (-1.0,-2.5) {$k=1$};
\node at (+2.0,-2.5) {$k=2$};
\draw [fill=black] (-4.0,-2.0) circle (0.05);
\draw [fill=black] (-1.0,-2.0) circle (0.05);
\draw [fill=black] (2.0,-2.0) circle (0.05);

@@

\begin{figure}[!htbp]
\begin{center}
\tikzstyle{line} = [thick]
\tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
\begin{tikzpicture}
\begin{scope}[scale=1]

@@

\end{scope}
\begin{scope}[xshift=0,yshift=3.0cm,scale=1]
    \node at (2,0) {\footnotesize $\scr{T} \equiv g_1(\x):\vx \in C
    \implies A_1\vx + \vb_1 + \delta_1$};
\end{scope}

@@

\end{scope}
\begin{scope}[xshift=0,yshift=4.0cm,scale=1]
    \node at (2,0) {\begin{minipage}{\textwidth}
    \footnotesize \begin{equation*}
        \scr{T} = \left\{
        \begin{array}{ll}
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_1\vx + \vb_1 + \delta_1\\
            g_2(\x):\vx \in C \land g'_2(\x):\vx \in C'_2 \implies A_2\vx + \vb_2 + \delta_2
        \end{array}
    \right.
\end{equation*}
\end{minipage}};
\end{scope}

@@

\begin{figure}[!htbp]
\begin{center}
\tikzstyle{line} = [thick]
\tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
\begin{tikzpicture}
\begin{scope}

@@

\begin{scope}[xshift=0,yshift=4.0cm,scale=1]
    \node at (4,0) {\begin{minipage}{\textwidth}
        \footnotesize \begin{equation*}
    \scr{T} = \left\{
        \begin{array}{ll}
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_1\vx + \vb_1 + \delta_1\\
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_2\vx + \vb_2 + \delta_2
        \end{array}
    \right.
\end{equation*}
\end{minipage}};
\end{scope}

@@

\inclfig[width=0.75\textwidth]{vdp_cont_traces.png}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.75\textwidth]{vdp_abs.png}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=\textwidth]{vdp_disc_map.png}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.40\textwidth]{vdp_graph.png}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}

>>>>

\begin{scope}[scale=0.8]
\draw [line] (-1.0,0) circle (0.5);
\draw [line] (-4.0,0) circle (0.5);
\draw [line] (2.0,1) circle (0.5);
\draw [line] (2.0,-1) circle (0.5);
\draw[arw] (-0.5,0) -- (1.5,1.0);
\draw[arw] (-0.5,0) -- (1.5,-1.0);
\draw[arw] (-3.5,0) -- (-1.5,0.0);
\node at (-4.0,0) {$C$};
\node at (-1.0,0) {$C'$};
\node at (2.0,1.0) {$C''_1$};
\node at (2.0,-1.0) {$C''_2$};
\draw [line] (2.0,-1) circle (0.5);
\draw[arw] (-5.0,-2.0) -- (3.0,-2.0);
\node at (-4.0,-2.5) {$k=0$};
\node at (-1.0,-2.5) {$k=1$};
\node at (+2.0,-2.5) {$k=2$};
\draw [fill=black] (-4.0,-2.0) circle (0.05);
\draw [fill=black] (-1.0,-2.0) circle (0.05);
\draw [fill=black] (2.0,-2.0) circle (0.05);

@@

\begin{figure}[!htbp]
\begin{center}
\tikzstyle{line} = [thick]
\tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
\begin{tikzpicture}
\begin{scope}[scale=0.5]

@@

\end{scope}
\begin{scope}[xshift=0,yshift=3.0cm,scale=0.5]
    \node at (2,0) {\footnotesize $\scr{T} \equiv g_1(\x):\vx \in C
    \implies A_1\vx + \vb_1 + \delta_1$};
\end{scope}

@@

\end{scope}
\begin{scope}[xshift=0,yshift=4.0cm,scale=0.5]
    \node at (2,0) {\begin{minipage}{\linewidth}
    \footnotesize \begin{equation*}
        \scr{T} = \left\{
        \begin{array}{ll}
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_1\vx + \vb_1 + \delta_1\\
            g_2(\x):\vx \in C \land g'_2(\x):\vx \in C'_2 \implies A_2\vx + \vb_2 + \delta_2
        \end{array}
    \right.
\end{equation*}
\end{minipage}};
\end{scope}

@@

\begin{figure}[!htbp]
\begin{center}
\tikzstyle{line} = [thick]
\tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
\begin{tikzpicture}
\begin{scope}[scale=0.5]

@@

\begin{scope}[xshift=0,yshift=4.0cm,scale=0.5]
    \node at (4,0) {\begin{minipage}{\linewidth}
        \footnotesize \begin{equation*}
    \scr{T} = \left\{
        \begin{array}{ll}
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_1\vx + \vb_1 + \delta_1\\
            g_1(\x):\vx \in C \land g'_1(\x):\vx \in C'_1 \implies A_2\vx + \vb_2 + \delta_2
        \end{array}
    \right.
\end{equation*}
\end{minipage}};
\end{scope}

@@

\inclfig[width=0.75\linewidth]{vdp_cont_traces.png}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.75\linewidth]{vdp_abs.png}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=\linewidth]{vdp_disc_map.png}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.40\linewidth]{vdp_graph.png}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}
